---
title: "Getting Started with binomial"
author: "Jacqueline Wood"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignettes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(binomial)
```


## Binomial

The package `"binomial"` is a package designed to model binomial distributions, to calculate summary statistics, and to visualize the distributions.


## Creating a `binvar`

In order to create a `binvar`, or a binomial random variable object:
```{r}
trials = 10
prob = 0.3

mybinvar <- bin_variable(trials,prob)
mybinvar
```

`bin_variable()` takes in two inputs: trials (number of trials) and prob (probability of success)

## Summary statistics

The `summary()` function gives you a nice output of summary statistics:
```{r}
summary(mybinvar)
```

## Plot of binomial distribution

You can plot a binomial distribution using this package too.

First, you create an object of the `bindis` (binomial distribution) class:
```{r}
mybindis <- bin_distribution(trials,prob)
mybindis
```

As shown above, `bin_distribution()` function returns a data frame with the probability distribution.

You can use the function `plot()` to create a barplot that displays the probability histogram of a binomial distribution object `bindis`.
```{r}
plot(mybindis)
```


## Plot of a Binomial Cumulative Distribution

You can plot a binomial cumulative distribution using this package as well.

First, you create an object of the `bincum` (binomial cumulative distribution) class:
```{r}
mybincum <- bin_cumulative(trials,prob)
mybincum
```

The `bin_cumulative()` function returns a data frame with the cumulative probability distribution.

You can use the function `plot()` to create a line graph of the cumulative distribution in an object `bincum`.
```{r}
plot(mybincum)
```

